Efficient spherical Convolutional Neural Networks with Healpix sampling for cosmological applications

### 2018-03-07 scnn.tex
edits in introduction

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{color}
\usepackage{url}
\usepackage{hyperref}
\usepackage{graphicx,array}
\usepackage{amsmath}

@@

a) Cosmology has a lot of spherical data. Our solution is easy to use and is based on the widely used healpix sampling.
b) It is the most efficient spherical convolution

@@

\begin{itemize}

	\item Efficient compression de-compression of 360 videos\cite{su2017learning}
	\item Analysis of spherical cosmological data such as the cosmic microwave background \cite{...}, already done in\cite{he2018analysis}.
\end{itemize}

Note that those neural networks are not restricted to the sphere and can be applied to any problem where we have data on a graph, such as social, biological or infrastructure networks.

>>>>

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{color}
\usepackage{url}
\usepackage{hyperref}
\usepackage{graphicx,array}
\usepackage{amsmath}
\usepackage{siunitx}

@@

a) Cosmology has a lot of spherical data. Our method is simple and easy to use. Moreover, it is based on the widely used healpix sampling.
b) It is the most efficient spherical convolution\footnote{\todo{provably? cannot be faster than O(n) without approximations, e.g. sketching}}, requiring only $O(n)$ operations, where $n$ is the number of points.

@@

The analysis of spherical cosmological data, such as the cosmic microwave background \cite{...}, as done in \cite{he2018analysis}, is the target application of our method.

While our method was developed with cosmology in mind, it can easily target any problem where data live on a sphere. Examples include, but are certainly not limited to, (i) efficient compression and decompression of \ang{360} videos (see \cite{su2017learning}), (ii) \todo{data analysis on planets? (climate, forecasting, temperature, wind)}, (iii) \todo{particle physics? (jets on detectors, but they are usually cylindrical)}, (iv) \todo{applications in Cohen's papers?}.

Finally, not that those neural networks are not restricted to the sphere and can be applied to any problem where we have data on a graph, such as social, biological or infrastructure networks [some citations, e.g. brain Alzeihmer, particle physics].
% the convolution is not restricted to the sphere, the coarsening/pooling is
